Hyperbolicity of Augmented Links in the Thickened Torus

### 2021-09-01 main.tex
added more nice diagrams

\begin{figure}[ht]
\input{bow-tie-modification.tikz}
\caption{Bow-tie modifications}
\label{f:bow-tie-modification}
\end{figure}

@@

\begin{figure}[ht]
\input{torihedra-graphs.tikz}
\caption{Constructing the top and bottom bow-tie graphs,
using bow-tie modifications}
\label{f:tori-decomp-graph}
\end{figure}

@@

Next we construct the graph that will define the ``top'' torihedron.
We view the link from the point at infinity from the top end
($\torus \times \{1\}$) of the thickened torus.
At each crossing of $K$,
push the top strand towards the bottom strand,
splitting the crossing edge into two
identical edges and spreading them apart as in
\figref{f:crossing-edges}.
%Figure \ref{fig:crossingArc}.
% (b).
%We push the link
%components to infinity and stretch the crossing edge so that we have flattened
%the link onto $\torus \times \{0\}$ except for the crossing circles,
%which remains perpendicular to the projection plane.

%Now place a disk on each crossing circle, so that the disk is bounded by
%the crossing circle.
Now for each crossing circle $c$, consider a spanning disk $B_c$;
$B_c$ intersects the projection plane $\torus \times \{0\}$
along the red segments in Figure \ref{fig:falGluings},
which consists of three edges.
We then cut $\torus \times I$ along $\torus \times \{0\}$ and
focus on the top half, $\torus \times [0,1)$.
(We will follow the same method on the
bottom half to obtain the second identical torihedron.)
The spanning disks we placed for each crossing circle are now cut in half
along the red segment.
Each half of the disk is now bounded by the
projection plane and the semi-circle arc of the crossing circle.
We push down on the crossing circle and split the half-disk into
two identical half-disks.
We then push the arc of each crossing circle to infinity,
collapsing them to ideal vertices.
We obtain two triangular faces which represent the half-disk which look like a
bow-tie as in Figure \ref{fig:falGluings} (a).
See Figures \ref{fig:step_one} to \ref{fig:top-bottom}
for an example.

\begin{figure}[ht]
\input{cut-slice-flatten.tikz}
\caption{Removing half-twists from augmented twist-regions}
\label{f:cut-slice-flatten}
\end{figure}

\begin{figure}
\centering
\begin{tabular}{cc}
\includegraphics [width=8cm]{falGluing1.png}&
\includegraphics [width=7cm]{falGluing2.png}\\
(a)&(b)
\end{tabular}
\caption{(a) Gluing of bow-ties without half-twists
(b) Gluing with half-twists}
\label{fig:falGluings}
\end{figure}

@@

\begin{quotation}
Suppose we cut the torus along a subset of edges in the dual graph
$\check{\Gamma}$, obtaining one or more pieces;
Then for any piece that is a disc,
the sum of $f$ over the edges in the boundary
of the piece is at least $2\pi$,
with equality if and only if the piece
contains exactly one vertex of $\Gamma$.
\end{quotation}

>>>>

\begin{figure}[ht]
\input{fig-bow-tie-modification.tikz}
\caption{Bow-tie modifications}
\label{f:bow-tie-modification}
\end{figure}

@@

\begin{figure}[ht]
\input{fig-torihedra-graphs.tikz}
\caption{Constructing the top and bottom bow-tie graphs,
using bow-tie modifications}
\label{f:tori-decomp-graph}
\end{figure}

@@

Next we construct the graph that will define the torihedra.
We view the link from the point at infinity from the top end
($\torus \times \{1\}$) of the thickened torus.
At each crossing of $K$,
push the top strand towards the bottom strand,
splitting the crossing edge into two
identical edges and spreading them apart as in
\figref{f:crossing-edges}.
%Figure \ref{fig:crossingArc}.
% (b).
%We push the link
%components to infinity and stretch the crossing edge so that we have flattened
%the link onto $\torus \times \{0\}$ except for the crossing circles,
%which remains perpendicular to the projection plane.

%Now place a disk on each crossing circle, so that the disk is bounded by
%the crossing circle.
Now for each crossing circle $c$, consider a spanning
(twice-punctured) disk $B_c$.
The following operations are depicted in \figref{f:cut-slice-flatten}.
$B_c$ intersects the projection plane $\torus \times \{0\}$,
cutting $B_c$ into two pieces $B_c^+,B_c^-$,
each being an ideal triangle.
We then slice along the disk $B_c$, turning it into two copies,
$B_c^{(1)},B_c^{(2)}$ (in no particular order);
each copy $B_c^{(j)}$ is also cut horizontally into two pieces,
$B_c^{(j),+},B_c^{(j),-}$.
We untwist all crossings in the twist region
which $c$ encircles,
rotating $B_c^{(j)}$ by $180^\circ$ for each crossing.
Then we flatten the disks;
the crossing circle is shrunk to a point,
as it is at infinity.

\begin{figure}[ht]
\input{fig-cut-slice-flatten.tikz}
\caption{Cut-slice-flatten}
\label{f:cut-slice-flatten}
\end{figure}

%%We cut $\torus \times I$ along $\torus \times \{0\}$ and
%%focus on the top half, $\torus \times [0,1)$.
%%(We will follow the same method on the
%%bottom half to obtain the second identical torihedron.)
%%The spanning disks we placed for each crossing circle are now
%%cut in half along the red segment.
%%Each half of the disk is now bounded by the
%%projection plane and the semi-circle arc of the crossing circle.
%%We push down on the crossing circle and split the half-disk into
%%two identical half-disks.
%%We then push the arc of each crossing circle to infinity,
%%collapsing them to ideal vertices.
%%We obtain two triangular faces which represent the half-disk which look like a
%%bow-tie as in Figure \ref{fig:falGluings} (a).
%%See Figures \ref{fig:step_one} to \ref{fig:top-bottom}
%%for an example.
%%
%%
%%\begin{figure}
%%\centering
%%\begin{tabular}{cc}
%%\includegraphics [width=8cm]{falGluing1.png}&
%%\includegraphics [width=7cm]{falGluing2.png}\\
%%(a)&(b)
%%\end{tabular}
%%\caption{(a) Gluing of bow-ties without half-twists
%%(b) Gluing with half-twists}
%%\label{fig:falGluings}
%%\end{figure}

@@

\begin{quotation}
Suppose we cut the torus along a subset of edges in the dual graph
$\check{\Gamma}$, obtaining one or more pieces;
Then for any piece that is a disk,
the sum of $f$ over the edges in the boundary
of the piece is at least $2\pi$,
with equality if and only if the piece
contains exactly one vertex of $\Gamma$.
\end{quotation}
